### 2022-04-26 ms/ms.rmd
Modify Labels

      # Plot a heatmap of N for each trait around the phylogeny.
      gheatmap(p1, data.matrix(matrix_data), offset = 1,  
               colnames_position="top", legend_title = "N", 
               colnames_angle=90, colnames_offset_y = 1, 
               hjust=0, font.size=2.5) + 
        scale_fill_viridis(alpha = 0.6) 
```

>>>>

      # Plot a heatmap of N for each trait around the phylogeny.
      gheatmap(p1, data.matrix(matrix_data), offset = 1,  
               colnames_position="bottom", legend_title = "N", 
               colnames_angle=90, colnames_offset_y = 2, 
               hjust=0, font.size=2.5, width = 0.25, colnames = FALSE) + 
        scale_fill_viridis(alpha = 0.6) + labs(fill="# of Effects")
```
